ODGI: understanding pangenome graphs

### 2021-10-18 manuscript/main.tex
Model: minor edits and comments

Such a graph can be constructed by a process like multiple sequence alignment \citep{Lee_2002,Grasso_2004}, but this partially-ordered graph cannot represent complex variation like inversions and cycles that occur at structural scales in genomes.
General approaches to building pangenome graphs transitively reduce an alignment between sequences to an equivalent, labeled sequence graph \citep{Kehr_2014,Garrison_2019_thesis}.
Current methods to build these graphs are still in development \citep{Li:2020,Armstrong:2020,pggb}, but they have largely settled on a common data model, represented in the Graphical Fragment Assembly (GFA) format \citep{GFA}).
%The improvement of these methods depends on tools that allow us to investigate
This standardization supports the development of a reference set of tools that operate on the pangenome graph model, while the need to understand the graphs made by these methods motivates it.

>>>>

Such a graph can be constructed by multiple sequence alignment \citep{Lee_2002,Grasso_2004}, but the resulting partially-ordered graph cannot represent complex variation like inversions and cycles that occur at structural scales in genomes.
General approaches to building pangenome graphs transitively reduce an alignment between sequences to an equivalent, labeled sequence graph \citep{Kehr_2014,Garrison_2019_thesis}.
Current methods to build these graphs are still in development \citep{Li:2020,Armstrong:2020,pggb}, but they have largely settled on a common data model, represented in the Graphical Fragment Assembly (GFA) format \citep{GFA}).
%The improvement of these methods depends on tools that allow us to investigate
This standardization supports the development of a reference set of tools that operate on the pangenome graph model, while the need to understand the graphs made by these methods motivates it. \FIXME{Sentence is a bit odd}.
